---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Hogwarts


I have created the "Hogwarts" package to learn how to develop an R package from scratch. It is a fun package that has two simple functions `letter()` and, `sorting_hat()` . As you insert your name as an argument, the function`letter()` gives you the decision whether you were admitted to the Hogwarts or not and `sorting_hat()` gives you the decision of which house you belong to; Griffindor, Slytherin, Ravenclaw or, Hufflepuff.

## Installation

You can install the development version of Hogwarts like so:

```r
install.packages("remotes")  # or devtools
remotes::install_github("MubarikaChowdhury/Hogwarts")
```

## Example

This is a basic example 

```{r example}
library(Hogwarts)
```

Example of using function `letter()`

```{r}
letter(name = "Mubarika")
```

Example of using function `sorting_hat()`

```{r}
sorting_hat(name = "Mubarika")
```



